Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-27 methods_paper/fabl-paper.tex
update.

@@

\hypertarget{posterior-sampling}{%
	\subsection{Gibbs Sampler}
	\label{gibbs_sampling}}
We work with the following factorization of the joint posterior distribution:

>>>>

\textcolor{red}{Are you handling missing values the way that Sadinle does? This isn't clear. It would he helpful to follow the Sadinle paper regarding structure as closely as possible given that it's very clear. I might recommend that you work on some details here regarding pages 12---13 as some important details are skipped over regarding what's random and observed that may not be obvious to the AE/reviewer.}

@@

\newpage
\textcolor{red}{RCS: I stopped here.}
\hypertarget{posterior-sampling}{%
	\subsection{Gibbs Sampler}
	\label{gibbs_sampling}}
We work with the following factorization of the joint posterior distribution:
